---
title: "SIMMAP and phylogenetic practices in R"
author: "Luben"
date: "30/08/2020"
output: html_document
---
Importing needed packages
```{r message=FALSE, include=FALSE}
library(ape)
library(phangorn)
library(phytools)
library(geiger)
library(magrittr)
library(mltools)
```
Testing ape and plotting some trees from newick text format
```{r}
tree.string = "(D,(C,(A,B)));"
tree.obj = read.tree(text = tree.string)
plot(tree.obj, no.margin = TRUE, edge.width = 2)
```
\ 
Now testing simmap from phytools in a given dataset
```{r}
# reading data, and plotting
X = read.csv("elopomorph.csv", row.names = 1)
elop.tree = read.tree("elopomorph.tre")

feed.mode = setNames(X[, 1], rownames(X))

# defining the variable classifying the feed mode of the current specie
head(X)
```
```{r}
# para fazer o gráfico 
# plotTree(elop.tree,type="fan",fsize=0.7,ftype="i",lwd=1)
# cols<-setNames(c("red","blue"),levels(feed.mode))
# tiplabels(pie=to.matrix(feed.mode[elop.tree$tip.label],
#     levels(feed.mode)),piecol=cols,cex=0.3)
# add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
#     y=0.8*par()$usr[3],fsize=0.8)
```
\ Adding estimated probabilitys to each internal nodes in tree
```{r}
# plotTree(elop.tree,type="fan",fsize=0.7,ftype="i",lwd=1)
#nodelabels(node=1:elop.tree$Nnode+Ntip(elop.tree),
#    pie=fitER$lik.anc, piecol=cols, cex=0.4)
#tiplabels(pie=to.matrix(feed.mode[elop.tree$tip.label],
#levels(feed.mode)), piecol=cols,cex=0.3)
#add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
#    y=0.8*par()$usr[3],fsize=0.8)
```
\ Making state matrix to simmap
```{r}
library(limSolve)
onehotencoder = function(data, index){
    nlvls = nlevels(data[, index])
    onehot = matrix(0, nrow = nrow(data), ncol = nlvls)
    factors = as.numeric(data[, index])
    for (i in 1:length(factors)){
        if(is.na(factors[i]) == TRUE){
            onehot[i, ] = rep(1/nlvls, nlvls)
        }else{
            onehot[i, factors[i]] = 1
        }
    }
    row.names(onehot) = row.names(data)
    colnames(onehot) = levels(data[, index])
    return(onehot)
}
feed.mode = onehotencoder(X, 1)
fit_discrete = make.simmap(elop.tree, feed.mode, model = "ARD", pi = "estimated")
xranges(G = t(as.matrix(fit_discrete$Q)), F = rep(1, 2), E = matrix(1, ncol = nrow(fit_discrete$Q), nrow = nrow(fit_discrete$Q)),
        H = c(0, 0))[, 1]
```
```{r}
mtree
```
```{r}
plot(mtree,cols,type="fan",fsize=0.8,ftype="i")
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=-max(nodeHeights(elop.tree)),fsize=0.8)
```
```{r}
plot(mtrees[[1]],cols,type="fan",fsize=0.6,ftype="i")
nodelabels(pie=pd$ace,piecol=cols,cex=0.4)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=-max(nodeHeights(elop.tree)),fsize=0.6)
```


\
Testing the ace in fastAnc in continuous data
```{r}
X = read.csv("elopomorph.csv", row.names = 1)
max.tl = setNames(X[, 2], rownames(X))


del.ind = match(NA, max.tl)
new_max.tl = max.tl[-del.ind]
del.ind_1 = match(NA, new_max.tl)
new_max.tl = new_max.tl[-del.ind]
del.ind_2 = match(NA, new_max.tl)
new_max.tl = new_max.tl[-del.ind_2]
del.ind_3 = match(NA, new_max.tl)
new_max.tl = new_max.tl[-del.ind_3]
new_max.tl
```
```{r}
fit = anc.ML(elop.tree, new_max.tl, model = "BM", tol = 1e-30)
fit$missing.x
fit$sig2
```
```{r}
plot(elop.tree)
```

\ 
All of this information above is related to a maximum likelihood estimation of the continuous character for each internal nodes of the given tree. We can plot a gradient tree as below:
```{r}
obj = contMap(elop.tree, max.tl, plot=FALSE)
plot(obj,type="fan",legend=0.7*max(nodeHeights(elop.tree)),
    fsize=c(0.5,0.9))
```