---
title: "Proof of concept"
output:
  html_document:
    df_print: paged
---
Importing needed packages
```{r message = F}
library(ape)
library(dendextend)
library(cluster)
library(tibble)
library(magrittr)
library(dplyr)
library(phytools)
library(mltools)
library(data.table)
library(factoextra)
source("C:/Users/lucru/Estatística_UFSCar/cv_cluster/modules/convert_to_parenthesis.R")
source("C:/Users/lucru/Estatística_UFSCar/cv_cluster/modules/cv_score.R")
library(tictoc)
library(mvMORPH)
library(tidyr)
library(MASS)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(gridBase)
library(grid)
library(clValid)
```
Here we have the interest of comparing the scatterplot, dendrogram and score of each hierarchical clustering method in order to do a proof of consent regarding our score, i.e., verify that our score makes sense in hierarchical clustering context. For that, me simulate the data with $n = 100$ sample points:
```{r}
set.seed(500)
n = 100
p = 2

Y = sample(c(0, 1), n, replace = TRUE, prob = c(0.5, 0.5))
mu_0 = c(0, 0)
mu_1 = c(2, 2)
S = diag(nrow = 2, ncol = 2)


X = matrix(nrow = n, ncol = p)
X[Y == 0, ] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
X[Y == 1, ] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)

sim.data = as.data.frame(cbind(X , Y))
sim.data$Y = as.factor(Y)
colnames(sim.data) = c("X1", "X2", "Y")
row.names(sim.data) = c(1:nrow(sim.data))
head(sim.data, 4)
```
Simulating the "wrong" data:
```{r}
X_3 = data.frame(X3 = rexp(n, 1))
head(X_3)
```
Scatterplot with "ground truth":
```{r}
sim.data %>%
          ggplot(aes(x = X1, y = X2, colour = Y)) +
          geom_point() +
          labs(x = "X1",
                y = "X2",
                colour = "Labels") +
          scale_colour_brewer(palette = "Set1") +
          theme_minimal()
```
\
Making the ploting function:
```{r}
plot_all_scores = function(original.data, cons.data, cl.list, dists = NA, nlvls = 2){
  list.names = names(cl.list)
  l = length(list.names)
  for(k in 1:l){
    hc.func = list.names[k]
    methods = cl.list[[hc.func]]
    m = length(methods)
    if(is.na(dists)){
      if(m > 0){
      for(c in 1:m){
        cons.hc = get(hc.func)(dist(scale(cons.data)), method = methods[c])
        cons.dend = convert_to_phylo(cons.hc)
        score.cons =  L_score(cons.dend, original.data[, -3])
        original.hc = get(hc.func)(dist(scale(original.data[, -3])), method = methods[c])
        original.dend = convert_to_phylo(original.hc)
        score.original = L_score(original.dend, original.data[, -3])
        p1.original = fviz_dend(original.hc, k = nlvls)
        factors = factor(cutree(original.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        p2.original = temp_data %>%
          ggplot(aes(x = X1, y = X2, colour = labels)) +
          geom_point() +
          labs(x = "X1",
                y = "X2",
                colour = "Labels") +
          scale_colour_brewer(palette = "Set1") +
          theme_minimal()
        p1.cons = fviz_dend(cons.hc, k = nlvls)
        factors = factor(cutree(cons.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        p2.cons = temp_data %>%
          ggplot(aes(x = X1, y = X2, colour = labels)) +
          geom_point() +
          labs(x = "X1",
                y = "X2",
                colour = "Labels") +
          scale_colour_brewer(palette = "Set1") +
          theme_minimal()
        t_grob1 = text_grob(paste0(hc.func,".", methods[c],
        " original data score: ", round(score.original, 4)), size = 12)
        t_grob2 = text_grob(paste0(hc.func,".", methods[c],
        " wrong data score: ", round(score.cons, 4)), size = 12)
        plot_1 = as_ggplot(t_grob1) + theme(plot.margin = margin(0,3,0,0, "cm"))
        plot_2 = as_ggplot(t_grob2) + theme(plot.margin = margin(0,3,0,0, "cm"))
        g1 = ggarrange(plot_1,ggarrange(p1.original, p2.original,
                       ncol = 2), nrow = 2, heights = c(1,5))
        g2 = ggarrange(plot_2, ggarrange(p1.cons, p2.cons,
                       ncol = 2), nrow = 2, heights = c(1,5))
        show(g1)
        show(g2)
      }
      }else{
        cons.hc = get(hc.func)(dist(scale(cons.data)))
        cons.dend = convert_to_phylo(cons.hc)
        score.cons =  L_score(cons.dend, original.data[, -3])
        original.hc = get(hc.funct)(dist(scale(original.data[, -3])))
        original.dend = convert_to_phylo(original.hc)
        score.original = L_score(original.dend, original.data[, -3])
        p1.original = fviz_dend(original.hc, k = nlvls)
        factors = factor(cutree(original.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        p2.original = temp_data %>%
          ggplot(aes(x = X1, y = X2, colour = labels)) +
          geom_point() +
          labs(x = "X1",
                y = "X2",
                colour = "Labels") +
          scale_colour_brewer(palette = "Set1") +
          theme_minimal()
        p1.cons = fviz_dend(cons.hc, k = nlvls)
        factors = factor(cutree(cons.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        p2.cons = temp_data %>%
          ggplot(aes(x = X1, y = X2, colour = labels)) +
          geom_point() +
          labs(x = "X1",
                y = "X2",
                colour = "Labels") +
          scale_colour_brewer(palette = "Set1") +
          theme_minimal()
        t_grob1 = text_grob(paste0(hc.func," original data score: ", 
                                   round(score.original, 4)))
        t_grob2 = text_grob(paste0(hc.func, " wrong data score: ", 
                                   round(score.cons, 4)))
        plot_1 = as_ggplot(t_grob1) + theme(plot.margin = margin(0,3,0,0, "cm"))
        plot_2 = as_ggplot(t_grob2) + theme(plot.margin = margin(0,3,0,0, "cm"))
        g1 = ggarrange(plot_1,ggarrange(p1.original, p2.original,
                       ncol = 2), nrow = 2, heights = c(1,5))
        g2 = ggarrange(plot_2, ggarrange(p1.cons, p2.cons,
                       ncol = 2), nrow = 2, heights = c(1,5))
        show(g1)
        show(g2)
      }
    }else{
        dists.length = length(dists)
        for(h in 1:dists.length){
        if(m > 0){
        for(c in (1:m)){
        cons.hc = get(hc.func)(dist(scale(cons.data), method = dists[h]), method = methods[c])
        cons.dend = convert_to_phylo(cons.hc)
        score.cons =  L_score(cons.dend, original.data[, -3])
        original.hc = get(hc.func)(dist(scale(original.data[, -3]), method = dists[h]), 
                             method = methods[c])
        original.dend = convert_to_phylo(original.hc)
        score.original = L_score(original.dend, original.data[, -3])
        p1.original = fviz_dend(original.hc, k = nlvls)
        factors = factor(cutree(original.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        p2.original = temp_data %>%
          ggplot(aes(x = X1, y = X2, colour = labels)) +
          geom_point() +
          labs(x = "X1",
                y = "X2",
                colour = "Labels") +
          scale_colour_brewer(palette = "Set1") +
          theme_minimal()
        p1.cons = fviz_dend(cons.hc, k = nlvls)
        factors = factor(cutree(cons.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        p2.cons = temp_data %>%
          ggplot(aes(x = X1, y = X2, colour = labels)) +
          geom_point() +
          labs(x = "X1",
                y = "X2",
                colour = "Labels") +
          scale_colour_brewer(palette = "Set1") +
          theme_minimal()
        t_grob1 =  text_grob(paste0(hc.func,".", methods[c],
          " original data with ",dists[h]," distance score: ",
                                                           round(score.original, 4)))
        t_grob2 = text_grob(paste0(hc.func,".", methods[c],
         " wrong data with ", dists[h], " distance score: ", round(score.cons, 4)))
        plot_1 = as_ggplot(t_grob1) + theme(plot.margin = margin(0,3,0,0, "cm"))
        plot_2 = as_ggplot(t_grob2) + theme(plot.margin = margin(0,3,0,0, "cm"))
        g1 = ggarrange(plot_1,ggarrange(p1.original, p2.original,
                       ncol = 2), nrow = 2, heights = c(1,5))
        g2 = ggarrange(plot_2, ggarrange(p1.cons, p2.cons,
                       ncol = 2), nrow = 2, heights = c(1,5))
        show(g1)
        show(g2)
      }
        }else{
        cons.hc = get(hc.func)(dist(scale(cons.data), method = dists[h]))
        cons.dend = convert_to_phylo(cons.hc)
        score.cons =  L_score(cons.dend, original.data[, -3])
        original.hc = hclust(dist(scale(original.data[, -3]), method = dists[h]))
        original.dend = convert_to_phylo(original.hc)
        score.original = L_score(original.dend, original.data[, -3])
        p1.original = fviz_dend(original.hc, k = nlvls)
        factors = factor(cutree(original.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        p2.original = temp_data %>%
          ggplot(aes(x = X1, y = X2, colour = labels)) +
          geom_point() +
          labs(x = "X1",
                y = "X2",
                colour = "Labels") +
          scale_colour_brewer(palette = "Set1") +
          theme_minimal()
        p1.cons = fviz_dend(cons.hc, k = nlvls)
        factors = factor(cutree(cons.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        p2.cons = temp_data %>%
          ggplot(aes(x = X1, y = X2, colour = labels)) +
          geom_point() +
          labs(x = "X1",
                y = "X2",
                colour = "Labels") +
          scale_colour_brewer(palette = "Set1") +
          theme_minimal()
        t_grob1 = text_grob(paste0(hc.func, " original data score: ", 
                                   round(score.original, 4)))
        t_grob2 =  text_grob(paste0(hc.func, " wrong data score: ", round(score.cons, 4)))
        plot_1 = as_ggplot(t_grob1) + theme(plot.margin = margin(0,3,0,0, "cm"))
        plot_2 = as_ggplot(t_grob2) + theme(plot.margin = margin(0,3,0,0, "cm"))
        g1 = ggarrange(plot_1,ggarrange(p1.original, p2.original,
                       ncol = 2), nrow = 2, heights = c(1,5))
        g2 = ggarrange(plot_2, ggarrange(p1.cons, p2.cons,
                       ncol = 2), nrow = 2, heights = c(1,5))
        show(g1)
        show(g2)
  }
  
        }
    }
  }
}
```
And now a list of all clustering methods and distances of interest:
```{r}
dists = c("euclidean", "manhattan", "canberra")
test.list = list(hclust = c("ward.D", "single","ward.D2", "average", "complete", "mcquitty", "median", "centroid"), agnes = c("weighted", "complete", "average", "ward"), diana = NULL)
```
```{r warning = F, results = 'hide'}
plot_all_scores(sim.data, X_3, test.list, dists)
```
\
Another interesting test to do is plot the dendrogram with the real labels than the chosen clusters and compare it to the same scatterplot. For that, we have the following example:
```{r}
par(mfrow = c(1, 2), mar = c(2, 1.5, 2, 2))
hc.func = hclust(dist(scale(sim.data[, -3])), method = "ward.D2")
dend = as.dendrogram(hc.func)
phylo = convert_to_phylo(hc.func)
order = as.numeric(phylo$tip.label)
labels = sim.data$Y[order]
colors = ifelse(labels == 1, "red", "blue")
dend2 = assign_values_to_leaves_edgePar(dend = dend, value = colors, edgePar = "col")
labels = cutree(hc.func, k = 2)
temp_data = sim.data[, -3]
temp_data$labels = factor(labels)
# plotando
plot(dend2)
plot(sim.data$X1, sim.data$X2, col = temp_data$labels, main = "Test title")
```
\
Generalizing that for the above list of clustering methods:
```{r warning = F, results = 'hide'}
plot_all_scores_2 = function(original.data, cons.data, cl.list, dists = NA, nlvls = 2){
  list.names = names(cl.list)
  l = length(list.names)
  par(mfrow = c(1, 2), mar = c(2, 1.5, 2, 2))
  for(k in 1:l){
    hc.func = list.names[k]
    methods = cl.list[[hc.func]]
    m = length(methods)
    if(is.na(dists)){
      if(m > 0){
      for(c in 1:m){
        # determining values of interest
        # cons
        cons.hc = get(hc.func)(dist(scale(cons.data)), method = methods[c])
        cons.dend = as.dendrogram(cons.hc)
        cons.phylo = convert_to_phylo(cons.hc)
        score.cons =  L_score(cons.phylo, original.data[, -3])
        order = as.numeric(cons.phylo$tip.label)
        cons.labels = original.data$Y[order]
        colors = ifelse(cons.labels == 1, "red", "blue")
        cons.dend2 = assign_values_to_leaves_edgePar(dend = cons.dend, value = 
                                                  colors, edgePar = "col")
        
        # original
        original.hc = get(hc.func)(dist(scale(original.data[, -3])), method = methods[c])
        original.dend = as.dendrogram(original.hc)
        original.phylo = convert_to_phylo(original.hc)
        score.original = L_score(original.phylo, original.data[, -3])
        order = as.numeric(original.phylo$tip.label)
        original.labels = original.data$Y[order]
        colors = ifelse(original.labels == 1, "red", "blue")
        original.dend2 = assign_values_to_leaves_edgePar(dend = original.dend, value = 
                                                  colors, edgePar = "col")
        
        
        # plotting for original
        plot(original.dend2)
        factors = factor(cutree(original.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        plot(temp_data$X1, temp_data$X2, col = temp_data$labels, 
             main = paste0(hc.func,".", methods[c], 
                      "original data \n score: ", round(score.original, 4)))
        
        # plotting for fake
        plot(cons.dend2)
        factors = factor(cutree(cons.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        plot(temp_data$X1, temp_data$X2, col = temp_data$labels, 
             main = paste0(hc.func,".", methods[c],
                          "wrong data  \n score: ", round(score.cons, 4)))
        
      }
      }else{
        
        # determining values of interest
        # cons
        cons.hc = get(hc.func)(dist(scale(cons.data)))
        cons.dend = as.dendrogram(cons.hc)
        cons.phylo = convert_to_phylo(cons.hc)
        score.cons =  L_score(cons.phylo, original.data[, -3])
        order = as.numeric(cons.phylo$tip.label)
        cons.labels = original.data$Y[order]
        colors = ifelse(cons.labels == 1, "red", "blue")
        cons.dend2 = assign_values_to_leaves_edgePar(dend = cons.dend, value = 
                                                  colors, edgePar = "col")
        
        # original
        original.hc = get(hc.func)(dist(scale(original.data[, -3])))
        original.dend = as.dendrogram(original.hc)
        original.phylo = convert_to_phylo(original.hc)
        score.original = L_score(original.phylo, original.data[, -3])
        order = as.numeric(original.phylo$tip.label)
        original.labels = original.data$Y[order]
        colors = ifelse(original.labels == 1, "red", "blue")
        original.dend2 = assign_values_to_leaves_edgePar(dend = original.dend, value = 
                                                  colors, edgePar = "col")
        
        
        # plotting for original
        plot(original.dend2)
        factors = factor(cutree(original.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        plot(temp_data$X1, temp_data$X2, col = temp_data$labels, 
             main = paste0(hc.func,
                              " original data \n score: ", round(score.original, 4)))
        
        # plotting for fake
        plot(cons.dend2)
        factors = factor(cutree(cons.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        plot(temp_data$X1, temp_data$X2, col = temp_data$labels, 
             main = paste0(hc.func,
                              " wrong data \n score: ", round(score.cons, 4)))
        
      }
    }else{
        dists.length = length(dists)
        for(h in 1:dists.length){
        if(m > 0){
        for(c in (1:m)){
        # determining values of interest
        # cons
        cons.hc = get(hc.func)(dist(scale(cons.data), method = dists[h]), method = methods[c])
        cons.dend = as.dendrogram(cons.hc)
        cons.phylo = convert_to_phylo(cons.hc)
        score.cons =  L_score(cons.phylo, original.data[, -3])
        order = as.numeric(cons.phylo$tip.label)
        cons.labels = original.data$Y[order]
        colors = ifelse(cons.labels == 1, "red", "blue")
        cons.dend2 = assign_values_to_leaves_edgePar(dend = cons.dend, value = 
                                                  colors, edgePar = "col")
        
        # original
        original.hc = get(hc.func)(dist(scale(original.data[, -3]), method = dists[h]), 
                                        method = methods[c])
        original.dend = as.dendrogram(original.hc)
        original.phylo = convert_to_phylo(original.hc)
        score.original = L_score(original.phylo, original.data[, -3])
        order = as.numeric(original.phylo$tip.label)
        original.labels = original.data$Y[order]
        colors = ifelse(original.labels == 1, "red", "blue")
        original.dend2 = assign_values_to_leaves_edgePar(dend = original.dend, value = 
                                                  colors, edgePar = "col")
        
        # plotting for original
        plot(original.dend2)
        factors = factor(cutree(original.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        plot(temp_data$X1, temp_data$X2, col = temp_data$labels, 
             main = paste0(hc.func,".", methods[c],
                            " original data with \n",dists[h]," distance score: ",
                              round(score.original, 4)))
        
        # plotting for fake
        plot(cons.dend2)
        factors = factor(cutree(cons.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        plot(temp_data$X1, temp_data$X2, col = temp_data$labels, 
             main  = paste0(hc.func,".", methods[c],
                  " wrong data with \n", dists[h], " distance score: ", round(score.cons, 4)))
        
      }
        }else{
          
          
          # determining values of interest
        # cons
        cons.hc = get(hc.func)(dist(scale(cons.data), method = dists[h]))
        cons.dend = as.dendrogram(cons.hc)
        cons.phylo = convert_to_phylo(cons.hc)
        score.cons =  L_score(cons.phylo, original.data[, -3])
        order = as.numeric(cons.phylo$tip.label)
        cons.labels = original.data$Y[order]
        colors = ifelse(cons.labels == 1, "red", "blue")
        cons.dend2 = assign_values_to_leaves_edgePar(dend = cons.dend, value = 
                                                  colors, edgePar = "col")
        
        # original
        original.hc = get(hc.func)(dist(scale(original.data[, -3]), method = dists[h]))
        original.dend = as.dendrogram(original.hc)
        original.phylo = convert_to_phylo(original.hc)
        score.original = L_score(original.phylo, original.data[, -3])
        order = as.numeric(original.phylo$tip.label)
        original.labels = original.data$Y[order]
        colors = ifelse(original.labels == 1, "red", "blue")
        original.dend2 = assign_values_to_leaves_edgePar(dend = original.dend, value = 
                                                  colors, edgePar = "col")
          
        
        # plotting for original
        plot(original.dend2)
        factors = factor(cutree(original.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        plot(temp_data$X1, temp_data$X2, col = temp_data$labels, 
             main = paste0(hc.func, 
                        " original data \n score: ", round(score.original, 4)))
        
        # plotting for fake
        plot(cons.dend2)
        factors = factor(cutree(cons.hc, k = nlvls))
        temp_data = original.data[, -3]
        temp_data$labels = factors
        plot(temp_data$X1, temp_data$X2, col = temp_data$labels, 
             main  = paste0(hc.func,".", methods[c],
                  " wrong data with \n", dists[h], " distance score: ", round(score.cons, 4)))
        

  }
  
        }
    }
  }
}
```
```{r}
dists = c("euclidean", "manhattan", "canberra")
test.list = list(hclust = c("ward.D", "single","ward.D2", "average", "complete", "mcquitty", "median", "centroid"), agnes = c("weighted", "complete", "average", "ward"), diana = NULL)
```
```{r warning = F, results = 'hide'}
plot_all_scores_2(sim.data, X_3, test.list, dists)
```
\
One other important thing to do is verify the alteration made to the score when we multiply each branch by a constant $c$. We can take the trees generated by hierarchical clustering with mccquity and complete method and multiply each branch by $10$ and $100$, assessing the effect of branch sizes in the score (brownian motiom): \
**Mcquitty modified trees and scores:**
```{r}
mcquitty.hc = hclust(dist(scale(sim.data[, -3])), 
                             method = "mcquitty")
mcquitty.dend = convert_to_phylo(mcquitty.hc)
# multiplying by 10
mcquitty.dend$edge.length = (mcquitty.dend$edge.length * 10)
score.mcquitty_10 = L_score(mcquitty.dend, sim.data[, -3])

# multiplying by 100
mcquitty.dend$edge.length = (mcquitty.dend$edge.length * 100)
score.mcquitty_100 = L_score(mcquitty.dend, sim.data[, -3])

cat("Mcquitty score for 10*branches: ", score.mcquitty_10, "\n")
cat("Mcquitty score for 100*branches: ", score.mcquitty_100)
```
**Complete modified trees and scores:**
```{r}
complete.hc = hclust(dist(scale(sim.data[, -3])), 
                             method = "complete")
complete.dend = convert_to_phylo(complete.hc)
# multiplying by 10
complete.dend$edge.length = (complete.dend$edge.length * 10)
score.complete_10 = L_score(complete.dend, sim.data[, -3])

# multiplying by 100
complete.dend$edge.length = (complete.dend$edge.length * 100)
score.complete_100 = L_score(complete.dend, sim.data[, -3])

cat("Complete score for 10*branches: ", score.complete_10, "\n")
cat("Complete score for 100*branches: ", score.complete_100)
```
So, according to these tests, there appear to be no difference between the scores, meaning that our score is invariant to scale modification, which is a good feature. We can also make a better separation between $(X_1, X_2, Y = 0)$ and $(X_1, X_2, Y= 1)$, repeating the proof of consent made above by several graphs: \
**Simulating more "separated" data**
```{r}
set.seed(500)
n = 100
p = 2

Y = sample(c(0, 1), n, replace = TRUE, prob = c(0.5, 0.5))
mu_0 = c(0, 0)
mu_1 = c(8, 8)
S = diag(nrow = 2, ncol = 2)


X = matrix(nrow = n, ncol = p)
X[Y == 0, ] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
X[Y == 1, ] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)

sim.data = as.data.frame(cbind(X , Y))
sim.data$Y = as.factor(Y)
colnames(sim.data) = c("X1", "X2", "Y")
row.names(sim.data) = c(1:nrow(sim.data))
head(sim.data, 4)

# wrong data
X_3 = data.frame(X3 = rexp(n, 1))
head(X_3)
```
**Plotting**
```{r}
plot_all_scores(sim.data, X_3, test.list, dists)
```
```{r}
plot_all_scores_2(sim.data, X_3, test.list, dists)
```
\
**Simulating data with 3 groups**
```{r}
set.seed(500)
n = 100
p = 2

Y = sample(c(0, 1, 2), n, replace = TRUE, prob = c(1/3, 1/3, 1/3))
mu_0 = c(1, 0)
mu_1 = c(2, 3)
mu_2 = c(-2, 6)
S = diag(nrow = 2, ncol = 2)


X = matrix(nrow = n, ncol = p)
X[Y == 0, ] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
X[Y == 1, ] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)
X[Y == 2, ] = round(mvrnorm(sum(Y == 2), mu_2, S), 4)

sim.data = as.data.frame(cbind(X , Y))
sim.data$Y = as.factor(Y)
colnames(sim.data) = c("X1", "X2", "Y")
row.names(sim.data) = c(1:nrow(sim.data))
head(sim.data, 4)

# wrong data
X_3 = data.frame(X3 = rexp(n, 1))
head(X_3)

# defining distances and methods again
dists = c("euclidean", "manhattan", "canberra")
test.list = list(hclust = c("ward.D", "single","ward.D2", "average", "complete", "mcquitty", "median", "centroid"), agnes = c("weighted", "complete", "average", "ward"), diana = NULL)
```
```{r}
sim.data %>%
          ggplot(aes(x = X1, y = X2, colour = Y)) +
          geom_point() +
          labs(x = "X1",
                y = "X2",
                colour = "Labels") +
          scale_colour_brewer(palette = "Set1") +
          theme_minimal()
```
\
Plotting all graphs for $k = 3$:
```{r}
plot_all_scores(sim.data, X_3, test.list, dists, nlvls = 3)
```




