---
title: "Some supervised learning tests for Dendrogram Score"
output:
  html_document:
    df_print: paged
  word_document: default
---
```{r global_options}
knitr::opts_chunk$set(echo = T, out.width = '85%', fig.align = "center", warning = F)
```
Importing needed packages
```{r}
getwd()
```

```{r message = FALSE}
library(ape)
library(dendextend)
library(cluster)
library(tibble)
library(magrittr)
library(dplyr)
library(phytools)
library(mltools)
library(data.table)
library(factoextra)
source("../modules/convert_to_parenthesis.R")
source("../modules/cv_score.R")
library(tictoc)
library(mvMORPH)
library(dplyr)
library(tidyr)
library(RColorBrewer)
library(MASS)
library(kableExtra)
library(plyr)
library(clValid)
```
First working with a simulated data set:
```{r}
set.seed(500)
n = 170
p = 2

Y = sample(c(0, 1), n, replace = TRUE, prob = c(0.5, 0.5))
mu_0 = c(0, 0)
mu_1 = c(1, 2)
S = cbind(c(2, 1), c(1, 3))


X = matrix(nrow = n, ncol = p)
X[Y == 0, ] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
X[Y == 1, ] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)

sim.data = as.data.frame(cbind(X , Y))
sim.data$Y = as.factor(Y)
colnames(sim.data) = c("X1", "X2", "Y")
row.names(sim.data) = c(1:nrow(sim.data))
head(sim.data, 4)
```
We can make a comparison function between a supervised learning prediction score computed into hierarchical clustering with ward.D2 method with our score:
```{r}
tic("Time of the supervised comparison")
comp = supervised_comparing(sim.data, clust = "hclust", clust_method = "ward.D2", test_index = 3)
comp
toc()
```
Testing the list input for supervised_comparing and cv_score algorithms:
```{r}
test.list = list(hclust = c("ward.D", "single","ward.D2", "average", "complete", "mcquitty", "median", "centroid"), agnes = c("weighted", "average", "ward"), diana = NA)
names(test.list)
test.list[[3]]
```
```{r}
paste0(names(test.list)[1], test.list[[1]][1])
```
Running all supervised comparisons:
```{r}
tic("Running time for all_supervised_comparing")
data.test = all_supervised_comparing(sim.data, clust = test.list, test_index = 3)
data.test
toc()
```
Graphing the comparisson:
```{r}
data.test %>%
  mutate(names = rownames(data.test)) %>% 
  ggplot(aes(x = V1, y = V3)) +
  geom_point(color = "red") +
  labs(x = "Proportion of hits",
       y = "Scores") +
  theme_minimal()
```
\
```{r}
sim.fom = FOM(sim.data[, -3], nlvls = 2, test.list)
```
```{r}
sim.fom
```
FOM versus score:
```{r}
data.test$FOM = sim.fom$V1
data.test %>%
  mutate(names = rownames(data.test)) %>% 
  ggplot(aes(x = FOM, y = V3)) +
  geom_point(color = "red") +
  labs(x = "FOM score",
       y = "Scores") +
  theme_minimal()
```

```{r}
dists = c("euclidean", "manhattan", "canberra")
tic("Running time for all_supervised_comparing")
data.test = all_supervised_comparing(sim.data, clust = test.list, test_index = 3, dist = dists)
data.test
toc()
```
Computing FOM:
```{r}
sim.fom = FOM(sim.data[, -3], nlvls = 2, test.list, dists = dists)
```
```{r}
sim.fom = sim.fom %>%
  dplyr::arrange(V2)

# arranging data.test
data.test = data.test %>%
  dplyr::arrange(V4)
sim.fom$V1 = as.numeric(sim.fom$V1)
sim.fom
```
Graphing the comparison acording to distance:
```{r echo=TRUE}
data.test = data.test %>%
  mutate(V1 = as.numeric(V1),
         V2 = as.numeric(V2),
         V3 = as.numeric(V3),
         V4 = as.factor(V4))
data.test %>%
  ggplot(aes(x = V1, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```
```{r}
data.test %>%
  ggplot(aes(x = V2, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```
```{r}
data.test$FOM = sim.fom$V1
data.test %>%
  ggplot(aes(x = FOM, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```

```{r}
cor(data.test$FOM, data.test$V3, method = "spearman")
```
Increasing sample size:
```{r}
set.seed(500)
n = 550
p = 2

Y = sample(c(0, 1), n, replace = TRUE, prob = c(0.5, 0.5))
mu_0 = c(0, 0)
mu_1 = c(1, 2)
S = cbind(c(2, 1), c(1, 3))


X = matrix(nrow = n, ncol = p)
X[Y == 0, ] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
X[Y == 1, ] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)

sim.data = as.data.frame(cbind(X , Y))
sim.data$Y = as.factor(Y)
colnames(sim.data) = c("X1", "X2", "Y")
row.names(sim.data) = c(1:nrow(sim.data))
head(sim.data, 4)
```
```{r}
dists = c("euclidean", "manhattan", "canberra")
tic("Running time for all_supervised_comparing")
data.test2 = all_supervised_comparing(sim.data, clust = test.list, test_index = 3, dist = dists)
data.test2
toc()
```
```{r}
sim.fom2 = FOM(sim.data[, -3], nlvls = 2, test.list, dists = dists)
sim.fom2 = sim.fom2 %>%
  dplyr::arrange(V2)

# arranging data.test
data.test2 = data.test %>%
  dplyr::arrange(V4)
sim.fom2$V1 = as.numeric(sim.fom2$V1)
sim.fom2
```
```{r}
data.test2 = data.test2 %>%
  mutate(V1 = as.numeric(V1),
         V2 = as.numeric(V2),
         V3 = as.numeric(V3),
         V4 = as.factor(V4))
data.test2 %>%
  ggplot(aes(x = V1, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```
```{r}
data.test2 %>%
  ggplot(aes(x = V2, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```
```{r}
data.test2$FOM = sim.fom2$V1
data.test2 %>%
  ggplot(aes(x = FOM, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```
```{r}
cor(data.test2$FOM, data.test2$V3, method = "spearman")
```
Repeating all the proccess for more separated data:
```{r}
set.seed(150)
n = 170
p = 2

Y = sample(c(0, 1), n, replace = TRUE, prob = c(0.5, 0.5))
mu_0 = c(0, 0)
mu_1 = c(6, 8)
S = diag(nrow = 2, ncol = 2)

X = matrix(nrow = n, ncol = p)
X[Y == 0, ] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
X[Y == 1, ] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)

sim.data = as.data.frame(cbind(X , Y))
sim.data$Y = as.factor(Y)
colnames(sim.data) = c("X1", "X2", "Y")
row.names(sim.data) = c(1:nrow(sim.data))
head(sim.data, 4)
```
```{r}
dists = c("euclidean", "manhattan", "canberra")
tic("Running time for all_supervised_comparing")
data.test = all_supervised_comparing(sim.data, clust = test.list, test_index = 3, dist = dists)
data.test
toc()
```
Computing FOM:
```{r}
sim.fom = FOM(sim.data[, -3], nlvls = 2, test.list, dists = dists)
```
```{r}
sim.fom = sim.fom %>%
  dplyr::arrange(V2)

# arranging data.test
data.test = data.test %>%
  dplyr::arrange(V4)
sim.fom$V1 = as.numeric(sim.fom$V1)
sim.fom
```
Graphing the comparison acording to distance:
```{r echo=TRUE}
data.test = data.test %>%
  mutate(V1 = as.numeric(V1),
         V2 = as.numeric(V2),
         V3 = as.numeric(V3),
         V4 = as.factor(V4))
data.test %>%
  ggplot(aes(x = V1, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```
```{r}
data.test$FOM = sim.fom$V1
data.test %>%
  ggplot(aes(x = FOM, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```

```{r}
cor(data.test$FOM, data.test$V3, method = "spearman")
```
Increasing sample size:
```{r}
set.seed(500)
n = 550
p = 2

Y = sample(c(0, 1), n, replace = TRUE, prob = c(0.5, 0.5))
mu_0 = c(0, 0)
mu_1 = c(6, 8)
S = diag(nrow = 2, ncol = 2)


X = matrix(nrow = n, ncol = p)
X[Y == 0, ] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
X[Y == 1, ] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)

sim.data = as.data.frame(cbind(X , Y))
sim.data$Y = as.factor(Y)
colnames(sim.data) = c("X1", "X2", "Y")
row.names(sim.data) = c(1:nrow(sim.data))
head(sim.data, 4)
```
```{r}
dists = c("euclidean", "manhattan", "canberra")
tic("Running time for all_supervised_comparing")
data.test2 = all_supervised_comparing(sim.data, clust = test.list, test_index = 3, dist = dists)
data.test2
toc()
```
```{r}
sim.fom2 = FOM(sim.data[, -3], nlvls = 2, test.list, dists = dists)
sim.fom2 = sim.fom2 %>%
  dplyr::arrange(V2)

# arranging data.test
data.test2 = data.test2 %>%
  dplyr::arrange(V4)
sim.fom2$V1 = as.numeric(sim.fom2$V1)
sim.fom2
```
```{r}
data.test2 %>%
  ggplot(aes(x = V1, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```
```{r}
data.test2$FOM = sim.fom2$V1
data.test2 %>%
  ggplot(aes(x = FOM, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```
```{r}
cor(data.test2$FOM, data.test2$V3, method = "spearman")
```

Testing iris dataset:
```{r}
flowers = iris
tic("Running time for all_supervised_comparing in iris dataset")
iris.test = all_supervised_comparing(flowers, clust = test.list, test_index = 5, dist = dists)
iris.test
toc()
```
```{r warning = F}
iris.fom = FOM(flowers[, -5], nlvls = 3, test.list, dists = dists)
```
```{r}
iris.fom = iris.fom %>%
  dplyr::arrange(V2)

# arranging data.test
iris.test = iris.test %>%
  dplyr::arrange(V4)
iris.fom$V1 = as.numeric(iris.fom$V1)
iris.fom
```
And then, graphing it:
**Proportion of hits versus Score values**
```{r echo = F}
iris.test = iris.test %>%
  mutate(V1 = as.numeric(V1),
         V2 = as.numeric(V2),
         V3 = as.numeric(V3),
         V4 = as.factor(V4))

iris.test %>%
  ggplot(aes(x = V1, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Score values 
       according to different distances") +
    theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5))+
  scale_colour_brewer(palette = "Set1")
```
\
**F1 versus Score values**
```{r}
iris.test %>%
  ggplot(aes(x = V2, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
```
\
```{r}
iris.test$FOM = iris.fom$V1
iris.test %>%
  ggplot(aes(x = FOM, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")

cor(iris.test$FOM, iris.test$V3, method = "kendall")
```
Testing supervisioned comparisson for cross validation score
```{r}
set.seed(500)
n = 170
p = 2

Y = sample(c(0, 1), n, replace = TRUE, prob = c(0.5, 0.5))
mu_0 = c(0, 0)
mu_1 = c(1, 2)
S = cbind(c(2, 1), c(1, 3))


X = matrix(nrow = n, ncol = p)
X[Y == 0, ] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
X[Y == 1, ] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)

sim.data = as.data.frame(cbind(X , Y))
sim.data$Y = as.factor(Y)
colnames(sim.data) = c("X1", "X2", "Y")
row.names(sim.data) = c(1:nrow(sim.data))
head(sim.data, 4)
```
```{r}
cl.list = list(hclust = c("single","ward.D2", "mcquitty", "average", "centroid", "complete",
                          "ward.D"), 
               agnes = c("weighted", "average"), diana = NA)
dists = c("euclidean", "manhattan", "canberra")
tic("Running time for all_supervised_comparing")
cv.data.test = supervised_comparing_L_cross_val(sim.data, cl.list, test_index = 3, 
                                             dists = dists)
head(cv.data.test, 10)
toc()
```
```{r}
cv.data.test %>%
  ggplot(aes(x = V1, y = hits, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Scores",
       y = "Proportion of hits",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5))+
  scale_colour_brewer(palette = "Set1") +
  coord_flip()
```
```{r}
cv.data.test %>%
  ggplot(aes(x = V1, y = F1, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Scores",
       y = "F1",
       colour = "Distances",
       title = "Scatterplot of F1 versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5))+
  scale_colour_brewer(palette = "Set1") +
  coord_flip()
```
```{r}
cv.data.test = cv.data.test %>%
  dplyr::arrange(V2)

cv.fom = FOM(sim.data[, -3], nlvls = 2, cl.list, dists = dists)
cv.fom$V1 = as.numeric(cv.fom$V1)
cv.fom = cv.fom %>%
  dplyr::arrange(V2)
cv.data.test$FOM = cv.fom$V1
```

```{r}
cv.data.test %>%
  ggplot(aes(x = V1, y = FOM, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Scores",
       y = "FOM score",
       colour = "Distances",
       title = "Scatterplot of FOM versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5))+
  scale_colour_brewer(palette = "Set1") +
  coord_flip()
```
\
To facilitate further investigations on several datasets, we can draft a function that make pairwise graphs of FOM and our score versus the other variables:
```{r}
# function for default score:
display.superv_comp = function(data, clust.list, test_index, dist = NA){
  k = nlevels(data[, test_index])
  data.test = all_supervised_comparing(data, clust = clust.list, test_index = test_index, dist = dist)
  fom.test = FOM(data[, -(test_index)], nlvls = k, clust.list, dist)
  # arranging datas
  fom.test = fom.test %>%
  dplyr::arrange(V2)
  data.test = data.test %>%
  dplyr::arrange(V4)
  fom.test$V1 = as.numeric(fom.test$V1)
  data.test$FOM = fom.test$V1
  
  # graphing and displaying correlations
  g1 = data.test %>%
  ggplot(aes(x = V1, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g2 = data.test %>%
  ggplot(aes(x = V2, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g3 = data.test %>%
  ggplot(aes(x = FOM, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g4 = data.test %>%
  ggplot(aes(x = V1, y = FOM, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g5 = data.test %>%
  ggplot(aes(x = V2, y = FOM, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  show(g1)
  show(g2)
  show(g3)
  cat("Correlations between score and other variables: \n")
  cat("Score versus proportion of hits: ", cor(data.test$V3, data.test$V1, method = "spearman"), "\n")
  cat("Score versus F1: ", cor(data.test$V3, data.test$V2, method = "spearman"), "\n")
  cat("Score versus FOM: ", cor(data.test$V3, data.test$FOM, method = "spearman"), "\n")
  
  show(g4)
  show(g5)
  cat("Correlations between FOM and other variables: \n")
  cat("FOM versus F1: ", cor(data.test$FOM, data.test$V2, method = "spearman"), "\n")
  cat("FOM versus proportion of hits: ", cor(data.test$FOM, data.test$V1, method = "spearman"), "\n")
  return(data.test)
}

CV_display.superv_comp = function(data, clust.list, test_index, dist = NA){
  k = nlevels(data[, test_index])
  data.test = supervised_comparing_L_cross_val(data, clust.list, test_index = test_index, dists = dist)
  fom.test = FOM(data[, -(test_index)], nlvls = k, clust.list, dist)
  # arranging datas
  
  data.test = data.test %>%
  dplyr::arrange(V2)
  
  fom.test$V1 = as.numeric(fom.test$V1)
  fom.test = fom.test %>%
  dplyr::arrange(V2)
  data.test$FOM = fom.test$V1
  
  # graphing and displaying correlations
  g1 = data.test %>%
  ggplot(aes(x = hits, y = V1, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g2 = data.test %>%
  ggplot(aes(x = F1, y = V1, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g3 = data.test %>%
  ggplot(aes(x = FOM, y = V1, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g4 = data.test %>%
  ggplot(aes(x = hits, y = FOM, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g5 = data.test %>%
  ggplot(aes(x = F1, y = FOM, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  show(g1)
  show(g2)
  show(g3)
  cat("Correlations between cross validated score and other variables: \n")
  cat("Score versus proportion of hits: ", cor(data.test$V1, data.test$hits), "\n")
  cat("Score versus F1: ", cor(data.test$V1, data.test$F1), "\n")
  cat("Score versus FOM: ", cor(data.test$V1, data.test$FOM), "\n")
  
  show(g4)
  show(g5)
  cat("Correlations between FOM and other variables: \n")
  cat("FOM versus F1: ", cor(data.test$FOM, data.test$hits), "\n")
  cat("FOM versus proportion of hits: ", cor(data.test$FOM, data.test$F1), "\n")
  return(data.test)
}

data.generator = function(n, mu_0, mu_1, p = 2, S = NULL, seed = 500){
  set.seed(seed)
  Y = sample(c(0, 1), n, replace = TRUE, prob = c(0.5, 0.5))
  if(is.null(S) == T) S = diag(nrow = p, ncol = p)
  X = matrix(nrow = n, ncol = p)
  X[Y == 0, ] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
  X[Y == 1, ] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)

  sim.data = as.data.frame(cbind(X , Y))
  sim.data$Y = as.factor(Y)
  if(p == 2){
  colnames(sim.data) = c("X1", "X2", "Y")}
  row.names(sim.data) = c(1:nrow(sim.data))
  return(sim.data)
}
```
Repeating simulation again:
```{r}
n = 170
p = 2
mu_0 = c(0, 0)
mu_1 = c(1, 2)
S = cbind(c(2, 1), c(1, 3))
sim.data = data.generator(n, mu_0, mu_1, S = S)
head(sim.data, 4)
```
```{r}
display.superv_comp(sim.data, test.list, test_index = 3, dist = dists)
```
For separated data:
```{r}
n = 170
p = 2
mu_0 = c(0, 0)
mu_1 = c(6, 8)
sim.data = data.generator(n, mu_0, mu_1, seed = 150)
head(sim.data, 4)
```
```{r}
display.superv_comp(sim.data, test.list, test_index = 3, dist = dists)
```
```{r}
n = 500
p = 2
mu_0 = c(0, 0)
mu_1 = c(2, 2)
sim.data = data.generator(n, mu_0, mu_1, seed = 150)
head(sim.data, 4)
```
```{r}
display.superv_comp(sim.data, test.list, test_index = 3, dist = dists)
```
```{r}
flowers = iris
display.superv_comp(flowers, test.list, test_index = 5, dist = dists)
```
```{r}
n = 170
p = 2
mu_0 = c(0, 0)
mu_1 = c(1, 2)
S = cbind(c(2, 1), c(1, 3))
sim.data = data.generator(n, mu_0, mu_1, S = S)
head(sim.data, 4)
```
```{r}
tic("Running time for cv_superv_comp")
CV_display.superv_comp(sim.data, test.list, test_index = 3, dist = dists)
toc()
```
Importing and testing real datasets: \
**Wheat seeds dataset**
```{r}
# wheat seeds dataset
wheat_data = read.delim("C:/Users/lucru/Estatística_UFSCar/cv_cluster/data/seeds_dataset.txt")
wheat_data$X1 = as.factor(wheat_data$X1)
head(wheat_data)
```
```{r}
tic("Running time for supervisioned comparisson in wheat seeds dataset")
display.superv_comp(wheat_data, test.list, test_index = 8, dist = dists)
toc()
```
\
**Prima indians diabetes dataset**
```{r}
# prima indians dataset
library(data.table)
prima_data <- as.data.frame(fread('https://raw.githubusercontent.com/jbrownlee/Datasets/master/pima-indians-diabetes.csv'))
prima_data$V9 = as.factor(prima_data$V9)
head(prima_data)
```
```{r}
tic("Running time for supervisioned comparisson in prima indians diabetes dataset")
display.superv_comp(prima_data, test.list, test_index = 9, dist = dists)
toc()
```
\
**Ionosphere dataset**
```{r}
ionosphere_data = as.data.frame(read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/ionosphere/ionosphere.data", sep = ","))
ionosphere_data$V35 = as.factor(ionosphere_data$V35)
head(ionosphere_data)
```
```{r}
tic("Running time for supervisioned comparisson in ionosphere dataset")
display.superv_comp(ionosphere_data, test.list, test_index = 35, dist = dists)
toc()
```





