---
title: "Tests envolving canberra distance"
author: "Luben"
date: "25/04/2021"
output: html_document
---
```{r global_options}
knitr::opts_chunk$set(echo = T, out.width = '85%', fig.align = "center", warning = F)
```
Importing needed packages
```{r message = FALSE}
library(ape)
library(dendextend)
library(cluster)
library(tibble)
library(magrittr)
library(dplyr)
library(phytools)
library(mltools)
library(data.table)
library(factoextra)
source("C:/Users/lucru/Estatística_UFSCar/cv_cluster/modules/convert_to_parenthesis.R")
source("C:/Users/lucru/Estatística_UFSCar/cv_cluster/modules/cv_score.R")
library(tictoc)
library(mvMORPH)
library(dplyr)
library(tidyr)
library(RColorBrewer)
library(MASS)
library(kableExtra)
library(plyr)
library(clValid)
```
To facilitate all investigations on several datasets (including simulated ones), we can draft a function that make pairwise graphs of FOM and our score versus the other variables:
```{r}
# function for default score:
display.superv_comp = function(data, clust.list, test_index, scale = F, dist = NA){
  k = nlevels(data[, test_index])
  data.test = all_supervised_comparing(data, clust = clust.list, test_index = test_index, dist = dist,
                                        scale = scale)
  print(data.test)
  if(length(dist) > 1){
  fom.test = FOM(data[, -(test_index)], nlvls = k, clust.list, dist,
                 scale = scale) 
  # arranging datas
  fom.test = fom.test %>%
  dplyr::arrange(V2)
  data.test = data.test %>%
  dplyr::arrange(V4)
  fom.test$V1 = as.numeric(fom.test$V1)
  data.test$FOM = fom.test$V1
  # dropping NA´s from V3
  data.test %<>% drop_na(V3)
  # graphing and displaying correlations
  g1 = data.test %>%
  ggplot(aes(x = V1, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g2 = data.test %>%
  ggplot(aes(x = V2, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g3 = data.test %>%
  ggplot(aes(x = FOM, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g4 = data.test %>%
  ggplot(aes(x = V1, y = FOM, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g5 = data.test %>%
  ggplot(aes(x = V2, y = FOM, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  show(g1)
  show(g2)
  show(g3)
  cat("Correlations between score and other variables: \n")
  cat("Score versus proportion of hits: ", cor(data.test$V3, data.test$V1, method = "spearman"), "\n")
  cat("Score versus F1: ", cor(data.test$V3, data.test$V2, method = "spearman"), "\n")
  cat("Score versus FOM: ", cor(data.test$V3, data.test$FOM, method = "spearman"), "\n")
  
  show(g4)
  show(g5)
  cat("Correlations between FOM and other variables: \n")
  cat("FOM versus F1: ", cor(data.test$FOM, data.test$V2, method = "spearman"), "\n")
  cat("FOM versus proportion of hits: ", cor(data.test$FOM, data.test$V1, method = "spearman"), "\n")
  return(data.test)
  }
}

CV_display.superv_comp = function(data, clust.list, test_index, dist = NA, scale = F, median = F){
  k = nlevels(data[, test_index])
  data.test = supervised_comparing_L_cross_val(data, clust.list, test_index = test_index, dists = dist,
                                               scale = scale, median = median)
  fom.test = FOM(data[, -(test_index)], nlvls = k, clust.list, dist, scale = scale)
  if(length(dist) > 1){
  # arranging datas
  data.test = data.test %>%
  dplyr::arrange(V2)
  
  fom.test$V1 = as.numeric(fom.test$V1)
  fom.test = fom.test %>%
  dplyr::arrange(V2)
  data.test$FOM = fom.test$V1
  
  # graphing and displaying correlations
  g1 = data.test %>%
  ggplot(aes(x = hits, y = V1, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Cross-Validated Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g2 = data.test %>%
  ggplot(aes(x = F1, y = V1, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus Cross-Validated Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g3 = data.test %>%
  ggplot(aes(x = FOM, y = V1, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Cross-Validated Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g4 = data.test %>%
  ggplot(aes(x = hits, y = FOM, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g5 = data.test %>%
  ggplot(aes(x = F1, y = FOM, colour = V2)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  show(g1)
  show(g2)
  show(g3)
  cat("Correlations between cross validated score and other variables: \n")
  cat("Cross validated score versus proportion of hits: ", cor(data.test$V1, data.test$hits, method = "spearman"), "\n")
  cat("Cross validated score versus F1: ", cor(data.test$V1, data.test$F1, method = "spearman"), "\n")
  cat("Cross validated score versus FOM: ", cor(data.test$V1, data.test$FOM, method = "spearman"), "\n")
  
  show(g4)
  show(g5)
  cat("Correlations between FOM and other variables: \n")
  cat("FOM versus proportion of hits: ", cor(data.test$FOM, data.test$hits, method = "spearman"), "\n")
  cat("FOM versus F1: ", cor(data.test$FOM, data.test$F1, method = "spearman"), "\n")
  return(data.test)
  }else{
  data.test$FOM = fom.test$V1
  
  # graphing and displaying correlations
  g1 = data.test %>%
  ggplot(aes(x = hits, y = V1)) +
  geom_point(colour = "blue") +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Cross-Validated Score values") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g2 = data.test %>%
  ggplot(aes(x = F1, y = V1)) +
  geom_point(colour = "blue") +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus Cross-Validated Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g3 = data.test %>%
  ggplot(aes(x = FOM, y = V1)) +
  geom_point(colour = "blue") +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Cross-Validated Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g4 = data.test %>%
  ggplot(aes(x = hits, y = FOM)) +
  geom_point(colour = "blue") +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g5 = data.test %>%
  ggplot(aes(x = F1, y = FOM)) +
  geom_point(colour = "blue") +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  show(g1)
  show(g2)
  show(g3)
  cat("Correlations between cross validated score and other variables: \n")
  cat("Cross validated score versus proportion of hits: ", cor(data.test$V1, data.test$hits, method = "spearman"), "\n")
  cat("Cross validated score versus F1: ", cor(data.test$V1, data.test$F1, method = "spearman"), "\n")
  cat("Cross validated score versus FOM: ", cor(data.test$V1, data.test$FOM, method = "spearman"), "\n")
  
  show(g4)
  show(g5)
  cat("Correlations between FOM and other variables: \n")
  cat("FOM versus proportion of hits: ", cor(data.test$FOM, data.test$hits, method = "spearman"), "\n")
  cat("FOM versus F1: ", cor(data.test$FOM, data.test$F1, method = "spearman"), "\n")
  return(data.test)
  }
}


display_data.superv_comp = function(data){
  # k = nlevels(data[, test_index])
  # data.test = all_supervised_comparing(data, clust = clust.list, test_index = test_index, dist = dist)
  data.test = data
  # fom.test = FOM(data[, -(test_index)], nlvls = k, clust.list, dist)
  # arranging datas
  # fom.test = fom.test %>%
  # dplyr::arrange(V2)
  # data.test = data.test %>%
  # dplyr::arrange(V4)
  # fom.test$V1 = as.numeric(fom.test$V1)
  # data.test$FOM = fom.test$V1
  
  # graphing and displaying correlations
  g1 = data.test %>%
  ggplot(aes(x = V1, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g2 = data.test %>%
  ggplot(aes(x = V2, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g3 = data.test %>%
  ggplot(aes(x = FOM, y = V3, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FOM score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of FOM versus Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g4 = data.test %>%
  ggplot(aes(x = V1, y = FOM, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Proportion of hits",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of proportion of hits versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  g5 = data.test %>%
  ggplot(aes(x = V2, y = FOM, colour = V4)) +
  geom_point() +
  theme_minimal() +
  labs(x = "F1 score",
       y = "Scores",
       colour = "Distances",
       title = "Scatterplot of F1 versus FOM Score values 
       according to different distances") +
  theme(text = element_text(size = 11, 
                            family ="serif"),
        plot.title = element_text(hjust = 0.5)) +
  scale_colour_brewer(palette = "Set1")
  
  show(g1)
  show(g2)
  show(g3)
  cat("Correlations between score and other variables: \n")
  cat("Score versus proportion of hits: ", cor(data.test$V3, data.test$V1, method = "spearman"), "\n")
  cat("Score versus F1: ", cor(data.test$V3, data.test$V2, method = "spearman"), "\n")
  cat("Score versus FOM: ", cor(data.test$V3, data.test$FOM, method = "spearman"), "\n")
  
  show(g4)
  show(g5)
  cat("Correlations between FOM and other variables: \n")
  cat("FOM versus F1: ", cor(data.test$FOM, data.test$V2, method = "spearman"), "\n")
  cat("FOM versus proportion of hits: ", cor(data.test$FOM, data.test$V1, method = "spearman"), "\n")
  return(data.test)
}

data.generator = function(n, mu_0, mu_1, p = 2, S = NULL, seed = 500){
  set.seed(seed)
  Y = sample(c(0, 1), n, replace = TRUE, prob = c(0.5, 0.5))
  if(is.null(S) == T) S = diag(nrow = p, ncol = p)
  X = matrix(nrow = n, ncol = p)
  X[Y == 0, ] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
  X[Y == 1, ] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)

  sim.data = as.data.frame(cbind(X , Y))
  sim.data$Y = as.factor(Y)
  if(p == 2){
  colnames(sim.data) = c("X1", "X2", "Y")}
  row.names(sim.data) = c(1:nrow(sim.data))
  return(sim.data)
}
```
Making all of the tests made in superv_comparisons:
```{r}
# excluding centroid
test.list = list(hclust = c("ward.D", "single","ward.D2", "average", "complete", "mcquitty", "median"), agnes = c("weighted", "average", "ward"), diana = NA)
dists = c("canberra")
```
```{r}
# fixing parameters
set.seed(122)
n = 170
p = 2
mu_0 = c(0, 0)
mu_1 = c(1, 2)
S = cbind(c(2, 1), c(1, 3))
sim.data = data.generator(n, mu_0, mu_1, S = S, seed = 250)
head(sim.data, 4)
```
```{r}
cv_sim.data = CV_display.superv_comp(sim.data, test.list, test_index = 3, dist = dists, scale = T)
cv_sim.data
```
```{r}
# excluding centroid
test.list = list(hclust = c("ward.D", "single","ward.D2", "average", "complete", "mcquitty", "median"), agnes = c("weighted", "average", "ward"), diana = NA)
dists = c("canberra", "euclidean", "manhattan")
```
```{r}
# fixing parameters
set.seed(122)
n = 170
p = 2
mu_0 = c(0, 0)
mu_1 = c(1, 2)
S = cbind(c(2, 1), c(1, 3))
sim.data = data.generator(n, mu_0, mu_1, S = S, seed = 250)
head(sim.data, 4)
```
```{r}
cv_sim.data = CV_display.superv_comp(sim.data, test.list, test_index = 3, dist = dists, scale = T)
cv_sim.data
```
Increasing sample size
```{r}
n = 280
p = 2
mu_0 = c(0, 0)
mu_1 = c(2, 2)
sim.data = data.generator(n, mu_0, mu_1, seed = 150)
head(sim.data, 4)
```
```{r}
cv_sim.test_2 = CV_display.superv_comp(sim.data, test.list, test_index = 3, dist = dists, 
                                       scale = T)
```
```{r}
mu_0 = c(2, 1)
mu_1 = c(8, 1)
S = rbind(c(1, 0.5), c(0.5,1))
n = 225
set.seed(600)

Y = sample(c(0,1), n, replace = T, prob = c(0.5, 0.5))
X = matrix(nrow = n, ncol = 2)
X[Y == 0,] = round(mvrnorm(sum(Y == 0), mu_0, S), 4)
X[Y == 1,] = round(mvrnorm(sum(Y == 1), mu_1, S), 4)
sim.data = as.data.frame(cbind(X, Y))
sim.data$Y = as.factor(Y)
colnames(sim.data) = c("X1", "X2", "Y")
```
```{r}
cv_sim.test_2 = CV_display.superv_comp(sim.data, test.list, test_index = 3, dist = dists, 
                                       scale = T)
```

\
Median:
```{r}
cv_sim.test_2 = CV_display.superv_comp(sim.data, test.list, test_index = 3, dist = dists, 
                                       scale = T, median = T)
```

```{r}
flowers = iris
cv_flowers.test = CV_display.superv_comp(flowers, test.list, test_index = 5, dist = dists,
                                         scale = T)
```
Pima data:
```{r}
n = 350
# prima indians dataset
library(data.table)
prima_data <- as.data.frame(fread('https://raw.githubusercontent.com/jbrownlee/Datasets/master/pima-indians-diabetes.csv'))
selected_rows = sample(1:nrow(prima_data), n, replace = F)
# selecting rows (too many samples)
prima_data$V9 = as.factor(prima_data$V9)
prima_data = prima_data[selected_rows, ]
row.names(prima_data) = 1:nrow(prima_data)
head(prima_data)
```
```{r}
tic("Running time for supervisioned comparisson in prima indians diabetes dataset")
cv_prima_data.test = CV_display.superv_comp(prima_data, test.list, test_index = 9, dist = dists,
                                         scale = T)
toc()
```
```{r}
# removing NaN
cv_prima_data.test %<>% na.omit(cv_prima_data.test)
cat("Correlations between cross validated score and other variables: \n")
  cat("Cross validated score versus proportion of hits: ", cor(cv_prima_data.test$V1, cv_prima_data.test$hits, method = "spearman"), "\n")
  cat("Cross validated score versus F1: ", cor(cv_prima_data.test$V1, cv_prima_data.test$F1, 
                                               method = "spearman"), "\n")
  cat("Cross validated score versus FOM: ", cor(cv_prima_data.test$V1, cv_prima_data.test$FOM, 
                                                method = "spearman"), "\n")
  
  cat("Correlations between FOM and other variables: \n")
  cat("FOM versus F1: ", cor(cv_prima_data.test$FOM, cv_prima_data.test$hits, 
                             method = "spearman"), "\n")
  cat("FOM versus proportion of hits: ", cor(cv_prima_data.test$FOM, cv_prima_data.test$F1,
                                             method = "spearman"), "\n")
```
```{r}
# wheat seeds dataset
wheat_data = read.delim("C:/Users/lucru/Estatística_UFSCar/cv_cluster/data/seeds_dataset.txt",
                        header = F)
wheat_data$V8 = as.factor(wheat_data$V8)
head(wheat_data)
```
```{r}
tic("Running time for supervisioned comparisson in wheat seeds dataset")
cv_wheat_data.test = CV_display.superv_comp(wheat_data, test.list, test_index = 8, dist = dists,
                                         scale = T)
toc()
```
```{r}
ionosphere_data = as.data.frame(read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/ionosphere/ionosphere.data", sep = ","))
ionosphere_data$V35 = as.factor(ionosphere_data$V35)
# droping second variable
ionosphere_data = ionosphere_data[, -2]
pca_ionosphere = prcomp(ionosphere_data[, -34], center = TRUE,scale. = TRUE)
summary(pca_ionosphere)

# selecting first 12 components
ionosphere_components = as.data.frame((pca_ionosphere$x)[, 1:12])
ionosphere_components$label = ionosphere_data[, 34]
head(ionosphere_components)
```
```{r}
tic("Running time for supervisioned comparisson in ionosphere dataset")
cv_ionosphere_data.test = CV_display.superv_comp(ionosphere_components, test.list, test_index = 13, 
                                           dist = dists, scale = T)
toc()
```
```{r}
# removing NaN
cv_ionosphere_data.test %<>% na.omit(cv_ionosphere_data.test)
cat("Correlations between cross validated score and other variables: \n")
  cat("Cross validated score versus proportion of hits: ", cor(cv_ionosphere_data.test$V1, cv_ionosphere_data.test$hits, method = "spearman"), "\n")
  cat("Cross validated score versus F1: ", cor(cv_ionosphere_data.test$V1, cv_ionosphere_data.test$F1, 
                                               method = "spearman"), "\n")
  cat("Cross validated score versus FOM: ", cor(cv_ionosphere_data.test$V1, cv_ionosphere_data.test$FOM, 
                                                method = "spearman"), "\n")
  
  cat("Correlations between FOM and other variables: \n")
  cat("FOM versus F1: ", cor(cv_ionosphere_data.test$FOM, cv_ionosphere_data.test$hits, 
                             method = "spearman"), "\n")
  cat("FOM versus proportion of hits: ", cor(cv_ionosphere_data.test$FOM, 
                                             cv_ionosphere_data.test$F1,
                                             method = "spearman"), "\n")
```
**Glass data**
```{r}
glass.data = as.data.frame(read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/glass/glass.data", sep = ","))
glass.data = glass.data[, -1]
glass.data$V11 = as.factor(glass.data$V11)
head(glass.data)
```
```{r}
tic("Running time for supervisioned comparisson in glass dataset")
cv_glass_data.test = CV_display.superv_comp(glass.data, test.list, test_index = 10, 
                                           dist = dists, scale = T)
toc()
```
\
**Haberman´s survival**
```{r}
haberman.data = as.data.frame(read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/haberman/haberman.data", sep = ","))
haberman.data$V4 = as.factor(haberman.data$V4)
head(haberman.data)
```
```{r}
tic("Running time for supervisioned comparisson in glass dataset")
cv_haberman_data.test = CV_display.superv_comp(haberman.data, test.list, test_index = 4, 
                                           dist = dists, scale = T)
toc()
```
\
**Wine data**
```{r}
wine.data = as.data.frame(read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/wine/wine.data", sep = ","))
wine.data$V1 = as.factor(wine.data$V1)
head(wine.data)
```
```{r}
tic("Running time for supervisioned comparisson in wine dataset")
cv_wine_data.test = CV_display.superv_comp(wine.data, test.list, test_index = 1, 
                                           dist = dists)
toc()
```
All canberra Median CVS:
```{r}
cv_sim.test_2 = CV_display.superv_comp(sim.data, test.list, test_index = 3, dist = dists, 
                                       scale = T, median = T)
```
```{r}
flowers = iris
cv_flowers.test = CV_display.superv_comp(flowers, test.list, test_index = 5, dist = dists,
                                         scale = T, median = T)
```
```{r}
tic("Running time for supervisioned comparisson in prima indians diabetes dataset")
cv_prima_data.test = CV_display.superv_comp(prima_data, test.list, test_index = 9, dist = dists,
                                         scale = T, median = T)
toc()
```
```{r}
tic("Running time for supervisioned comparisson in wheat seeds dataset")
cv_wheat_data.test = CV_display.superv_comp(wheat_data, test.list, test_index = 8, dist = dists,
                                         scale = T, median = T)
toc()
```
```{r}
tic("Running time for supervisioned comparisson in ionosphere dataset")
cv_ionosphere_data.test = CV_display.superv_comp(ionosphere_components, test.list, test_index = 13, 
                                           dist = dists, scale = T, median = T)
toc()
```
```{r}
tic("Running time for supervisioned comparisson in glass dataset")
cv_glass_data.test = CV_display.superv_comp(glass.data, test.list, test_index = 10, 
                                           dist = dists, scale = T, median = T)
toc()
```
```{r}
tic("Running time for supervisioned comparisson in glass dataset")
cv_haberman_data.test = CV_display.superv_comp(haberman.data, test.list, test_index = 4, 
                                           dist = dists, scale = T, median = T)
toc()
```
```{r}
tic("Running time for supervisioned comparisson in wine dataset")
cv_wine_data.test = CV_display.superv_comp(wine.data, test.list, test_index = 1, 
                                           dist = dists)
toc()
```
Taking only canberra outputs and plotting trees cut at certain levels for each dataset:
```{r}

# fixing parameters
set.seed(122)
n = 170
p = 2
mu_0 = c(0, 0)
mu_1 = c(1, 2)
S = cbind(c(2, 1), c(1, 3))
sim.data = data.generator(n, mu_0, mu_1, S = S, seed = 250)
head(sim.data, 4)

# excluding centroid
test.list = list(hclust = c("ward.D", "single","ward.D2", "average", "complete", "mcquitty", "median"), agnes = c("weighted", "average", "ward"), diana = NA)
dist = c("canberra")
```
```{r}
plot_all_trees = function(quant_data, cl.list, dist, factor){
  list.names = names(cl.list)
  l = length(list.names)
  scores = L_cross_val(quant_data,  cl.list, dists = dist, scale = T)
  lvls = levels(factor)
  nlvls= length(lvls)
  relab_y = mapvalues(factor, from = lvls, to = 1:nlvls)
  new_lvls = levels(relab_y)
  for(k in 1:l){
    hc.func = list.names[k]
    methods = cl.list[[hc.func]]
    m = length(methods)
      if(is.na(methods) == F){
      for(c in 1:m){
        original.hc = get(hc.func)(dist(scale(quant_data)), method = methods[c])
        original.dend = convert_to_phylo(original.hc)
        name.row = paste0(hc.func, ".", methods[c])
        # adicionar F1 aki
        clusters = factor(cutree(original.hc, k = nlvls))
        perms = permutations(n = nlvls, r = nlvls,v = new_lvls)
        hits = numeric(nrow(perms))
        clusts = matrix(0, nrow = nrow(perms), ncol = length(clusters))
        for(i in (1:nrow(perms))){
              new_clust = mapvalues(clusters, from = levels(clusters), to = perms[i, ])
              clusts[i, ] = new_clust
              temp_hit = (sum(new_clust == relab_y)/length(relab_y))
              hits[i] = temp_hit
        }
        max.index = which.max(hits)
        F1 = F1_Score(relab_y, clusts[max.index, ])
        score.original = scores[name.row, ]
        p1.original = fviz_dend(original.hc, k = nlvls) +
          labs(title = paste0(hc.func,".", methods[c],
        " cv score: ", round(score.original, 4), " \n F1:", round(F1, 4)))
        show(p1.original)
        
        # original
        order = original.dend$tip.label
        original.labels = relab_y[as.numeric(order)]
        if(nlvls == 2){
          b = order[original.labels == "2"]
          tt<-paintBranches(original.dend, edge = sapply(b, match, original.dend$tip.label),
          state = "2", anc.state = "1")
          cols = setNames(c("blue", "red"), c("1", "2"))
          plot(tt, colors = cols, lwd = 4, split.vertical = T, ftype = "i")
        }else{
          b = order[original.labels == "2"]
          c = order[original.labels == "3"]
          tt<-paintBranches(original.dend, edge=sapply(b,match, original.dend$tip.label),
          state = "2", anc.state = "1")
          tt<-paintBranches(tt, edge = sapply(c,match, original.dend$tip.label),
            state = "3")
          cols = setNames(c("blue", "red", "green"), c("1", "2", "3"))
          plot(tt, colors = cols, lwd = 0.65, split.vertical = T, ftype = "i")
        }
      }
      }else{
       original.hc = get(hc.func)(dist(scale(quant_data)))
        original.dend = convert_to_phylo(original.hc)
        
        name.row = paste0(hc.func)
        # adicionar F1 aki
        clusters = factor(cutree(original.hc, k = nlvls))
        perms = permutations(n = nlvls, r = nlvls,v = new_lvls)
        hits = numeric(nrow(perms))
        clusts = matrix(0, nrow = nrow(perms), ncol = length(clusters))
        for(i in (1:nrow(perms))){
              new_clust = mapvalues(clusters, from = levels(clusters), to = perms[i, ])
              clusts[i, ] = new_clust
              temp_hit = (sum(new_clust == relab_y)/length(relab_y))
              hits[i] = temp_hit
        }
        max.index = which.max(hits)
        F1 = F1_Score(relab_y, clusts[max.index, ])
        score.original = scores[name.row, ]
        p1.original = fviz_dend(original.hc, k = nlvls) +
          labs(title = paste0(hc.func,
        " cv score: ", round(score.original, 4), " \n F1:", round(F1, 4)))
        show(p1.original) 
        
       # original
        order = original.dend$tip.label
        original.labels = relab_y[as.numeric(order)]
        if(nlvls == 2){
          b = order[original.labels == "2"]
          tt<-paintBranches(original.dend, edge = sapply(b, match, original.dend$tip.label),
          state = "2", anc.state = "1")
          cols = setNames(c("blue", "red"), c("1", "2"))
          plot(tt, colors = cols, lwd = 4, split.vertical = T, ftype = "i")
        }else{
          b = order[original.labels == "2"]
          c = order[original.labels == "3"]
          tt<-paintBranches(original.dend, edge=sapply(b,match, original.dend$tip.label),
          state = "2", anc.state = "1")
          tt<-paintBranches(tt, edge = sapply(c,match, original.dend$tip.label),
            state = "3")
          cols = setNames(c("blue", "red", "green"), c("1", "2", "3"))
          plot(tt, colors = cols, lwd = 0.65, split.vertical = T, ftype = "i")
        }
      }
      }
}

plot_all_trees(sim.data[, -3], test.list, dist, factor = sim.data[, 3])

```
```{r}
n = 280
p = 2
mu_0 = c(0, 0)
mu_1 = c(2, 2)
sim.data = data.generator(n, mu_0, mu_1, seed = 150)
head(sim.data, 4)
plot_all_trees(sim.data[, -3], test.list, dist, factor = sim.data[, 3])
```
```{r}
flowers = iris
plot_all_trees(flowers[, -5], test.list, dist, factor = flowers[, 5])
```
Pima data:
```{r}
n = 350
# prima indians dataset
library(data.table)
prima_data <- as.data.frame(fread('https://raw.githubusercontent.com/jbrownlee/Datasets/master/pima-indians-diabetes.csv'))
selected_rows = sample(1:nrow(prima_data), n, replace = F)
# selecting rows (too many samples)
prima_data$V9 = as.factor(prima_data$V9)
prima_data = prima_data[selected_rows, ]
row.names(prima_data) = 1:nrow(prima_data)
plot_all_trees(prima_data[, -9], test.list, dist, factor = prima_data[, 9])
```
```{r}
# wheat seeds dataset
wheat_data = read.delim("C:/Users/lucru/Estatística_UFSCar/cv_cluster/data/seeds_dataset.txt",
                        header = F)
wheat_data$V8 = as.factor(wheat_data$V8)
plot_all_trees(wheat_data[, -8], test.list, dist, factor = wheat_data[, 8])
```
```{r}
ionosphere_data = as.data.frame(read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/ionosphere/ionosphere.data", sep = ","))
ionosphere_data$V35 = as.factor(ionosphere_data$V35)
# droping second variable
ionosphere_data = ionosphere_data[, -2]
pca_ionosphere = prcomp(ionosphere_data[, -34], center = TRUE,scale. = TRUE)
summary(pca_ionosphere)

# selecting first 12 components
ionosphere_components = as.data.frame((pca_ionosphere$x)[, 1:12])
ionosphere_components$label = ionosphere_data[, 34]
head(ionosphere_components)
```
```{r}
plot_all_trees(ionosphere_components[, -13], test.list, dist, factor = ionosphere_components[, 13])
```
**Glass data**
```{r}
glass.data = as.data.frame(read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/glass/glass.data", sep = ","))
glass.data = glass.data[, -1]
glass.data$V11 = as.factor(glass.data$V11)
plot_all_trees(glass.data[, -10], test.list, dist, factor = glass.data[, 10])
```
\
**Haberman´s survival**
```{r}
haberman.data = as.data.frame(read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/haberman/haberman.data", sep = ","))
haberman.data$V4 = as.factor(haberman.data$V4)
head(haberman.data)
plot_all_trees(haberman.data[, -4], test.list, dist, factor = haberman.data[, 4])
```
\
**Wine data**
```{r}
wine.data = as.data.frame(read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/wine/wine.data", sep = ","))
wine.data$V1 = as.factor(wine.data$V1)
plot_all_trees(wine.data[, -1], test.list, dist, factor = wine.data[, 1])
```
\
All three distances median cv:
```{r}
# excluding centroid
test.list = list(hclust = c("ward.D", "single","ward.D2", "average", "complete", "mcquitty", "median"), agnes = c("weighted", "average", "ward"), diana = NA)
dists = c("canberra", "euclidean", "manhattan")
```
```{r}
cv_sim.test_2 = CV_display.superv_comp(sim.data, test.list, test_index = 3, dist = dists, 
                                       scale = T, median = T)
```
```{r}
flowers = iris
cv_flowers.test = CV_display.superv_comp(flowers, test.list, test_index = 5, dist = dists,
                                         scale = T, median = T)
```
```{r}
tic("Running time for supervisioned comparisson in prima indians diabetes dataset")
cv_prima_data.test = CV_display.superv_comp(prima_data, test.list, test_index = 9, dist = dists,
                                         scale = T, median = T)
toc()
```
```{r}
tic("Running time for supervisioned comparisson in wheat seeds dataset")
cv_wheat_data.test = CV_display.superv_comp(wheat_data, test.list, test_index = 8, dist = dists,
                                         scale = T, median = T)
toc()
```
```{r}
tic("Running time for supervisioned comparisson in ionosphere dataset")
cv_ionosphere_data.test = CV_display.superv_comp(ionosphere_components, test.list, test_index = 13, 
                                           dist = dists, scale = T, median = T)
toc()
```
```{r}
tic("Running time for supervisioned comparisson in glass dataset")
cv_glass_data.test = CV_display.superv_comp(glass.data, test.list, test_index = 10, 
                                           dist = dists, scale = T, median = T)
toc()
```
```{r}
tic("Running time for supervisioned comparisson in glass dataset")
cv_haberman_data.test = CV_display.superv_comp(haberman.data, test.list, test_index = 4, 
                                           dist = dists, scale = T, median = T)
toc()
```
```{r}
tic("Running time for supervisioned comparisson in wine dataset")
cv_wine_data.test = CV_display.superv_comp(wine.data, test.list, test_index = 1, 
                                           dist = dists)
toc()
```






















